### 2012-10-02 inst/examples/multiple_uncertainty.Rmd
small multiple uncertainty: working example! Uses matrix approach in R/SDP_multiple_uncertainty.R

`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`

``` {r  setup, echo=FALSE, cache=FALSE}
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
theme_publish <- theme_set(theme_bw(14))
theme_publish <- theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
        panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
        plot.background=theme_blank(), legend.title=theme_blank())
````

@@

``` {r }
xmin <- 0
xmax <- 150
grid_n <- 20
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .1
sigma_m <- 0
sigma_i <- 0
````

@@

```{r deterministic}
pdfn_old <- function(P,s) dunif(P, 1-s, 1+s)
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn_old)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

>>>>

`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="cache/multiple_uncertainty/", verbose=TRUE or`

``` {r  setup, echo=FALSE, cache=FALSE}
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
theme_publish <- theme_set(theme_bw(14))
theme_publish <- theme_update(
        # panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
        legend.title=theme_blank(), 
        panel.background = theme_rect(fill = "transparent",colour = NA), 
        plot.background = theme_rect(fill = "transparent",colour = NA))
````

@@

``` {r }
xmin <- 0
xmax <- 150
grid_n <- 150
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- 0.5
sigma_m <- 0.5
sigma_i <- 0.5
````

@@

```{r deterministic}
det_mat <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, 0, 0)
det <- find_dp_optim(det_mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````
